### 2017-02-27 backmatter.tex
Edit done

\appendix
\renewcommand{\chaptername}{Appendix}
\chapter{\texorpdfstring{Overview of systematic uncertainties in the MSSM \AHtotautau analysis}{Overview of systematic uncertainties in the MSSM A/H to tautau analysis}}
\label{appendix:uncerts}
An overview of the systematic uncertainties that are applied in the MSSM \AHtotautau analysis (chapter \ref{chap:mssm})
are summarised in this appendix. The uncertainties are given in
table \ref{tab:SystematicUncertainties_mt} for the $\mu\tau_h$
channel, in table \ref{tab:SystematicUncertainties_et} for the $e\tau_h$ channel,
in table \ref{tab:SystematicUncertainties_tt} for the $\tau_h\tau_h$ channel and
in table \ref{tab:SystematicUncertainties_em} for the $e\mu$ channel. Additionally,
the systematic uncertainties for the $Z\rightarrow\mumu$ control region are shown
in table \ref{tab:SystematicUncertainties_zmm}. Correlations are also indicated.
Some of the uncertainties
are different for different processes, where this is the case ranges are given.
Uncertainties marked "Fully correlated" are correlated between the different
decay channels and event categories, those marked "Fully uncorrelated" are
uncorrelated between the different decay channels and event categories. "Cats:C,chns:U"
indicates that the uncertainty is correlated between categories but uncorrelated between
the different decay channels. For brevity the backgrounds are denoted with shorthand notations.
`ZTT' indicates the \Ztautau component. 'ZJ' is reserved for the \Zellell background
in which the tau is faked by a jet. The \Zellell background in which the tau is faked
by an electron or muon is indicated as 'ZL'. `W' indicates the \Wjets process. `TT' denotes
the \ttbar background, with  `TTT' and `TTJ'
indicating the \ttbar background with real hadronic taus and without real hadronic taus, respectively. 
The di-boson and single-top backgrounds are denoted `VV', with
`VVT' and `VVJ' indicating the di-boson plus single-top background with real hadronic taus
and without real hadronic taus, respectively. The QCD multijet background is denoted `QCD'.
\input{MSSM/UncOv}

>>>>

\appendix
\renewcommand{\chaptername}{Appendix}
\chapter{\texorpdfstring{Systematic uncertainties in the MSSM \AHtotautau analysis}{Overview of systematic uncertainties in the MSSM A/H to tautau analysis}}
\label{appendix:uncerts}
An overview of the systematic uncertainties that are applied in the MSSM \AHtotautau analysis (chapter \ref{chap:mssm})
are summarised in this appendix. The uncertainties are given in
table \ref{tab:SystematicUncertainties_mt} for the $\mu\tau_h$
channel, in table \ref{tab:SystematicUncertainties_et} for the $e\tau_h$ channel,
in table \ref{tab:SystematicUncertainties_tt} for the $\tau_h\tau_h$ channel and
in table \ref{tab:SystematicUncertainties_em} for the $e\mu$ channel. Additionally,
the systematic uncertainties for the $Z\rightarrow\mumu$ control region are shown
in table \ref{tab:SystematicUncertainties_zmm}. Correlations are also indicated.
Some of the uncertainties
are different for different processes, where this is the case ranges are given.
Uncertainties marked "Fully correlated" are correlated between the different
decay channels and event categories, those marked "Fully uncorrelated" are
uncorrelated between the different decay channels and event categories. "Cats:C,chns:U"
indicates that the uncertainty is correlated between categories but uncorrelated between
the different decay channels. For brevity the backgrounds are denoted with shorthand notations.
`ZTT' indicates the \Ztautau component. 'ZJ' is reserved for the \Zellell background
in which the tau is faked by a jet. The \Zellell background in which the tau is faked
by an electron or muon is indicated as 'ZL'. `W' indicates the \Wjets process. `TT' denotes
the \ttbar background, with  `TTT' and `TTJ'
indicating the \ttbar background with real hadronic taus and without real hadronic taus, respectively. 
The di-boson and single-top backgrounds are denoted `VV', with
`VVT' and `VVJ' indicating the di-boson plus single-top background with real hadronic taus
and without real hadronic taus, respectively. The QCD multijet background is denoted `QCD'.
\input{MSSM/UncOv}

### 2017-02-27 frontmatter.tex
Edit done

% Abstract
\begin{abstract}%[\smaller \thetitle\\ \vspace*{1cm} \smaller {\theauthor}]
  %\thispagestyle{empty}
The Compact Muon Solenoid (CMS) detector is a general-purpose detector located at the Large Hadron
Collider at CERN. It was designed to test the predictions of the standard model 
and to search for the Higgs boson in addition to searches for new physics beyond
the standard model.
The analyses presented in this thesis are searches for neutral
Higgs bosons with tau leptons in the final state. These searches use proton-proton collision data recorded
by CMS during 2012, 2015 and 2016. The searches are performed in the
context of the minimal supersymmetric standard model (MSSM). One of the analyses, using $19.7\,\invfb$ 
of data collected
during 2012 at $\sqrt{s}=8\,\TeV$, is a search for a heavy neutral Higgs boson
decaying into two $125\,\GeV$ Higgs bosons with standard model-like properties,
with two b-quarks and two tau leptons in the final state. The other analyses use 
$2.3\,\invfb$ of data collected during 2015 and $12.9\,\invfb$ of data collected during 2016, both
at $\sqrt{s}=13\,\TeV$. These are searches for neutral MSSM
Higgs bosons in the mass range of \mbox{$90\,\GeV$--$3.2\,\TeV$} directly decaying
into pairs of tau leptons. 
No significant excess is observed in any of the searches. Upper limits at the 95\% confidence 
level are set on the cross section times branching ratio for the production of Higgs bosons in the \ac{MSSM}.
In addition, limits are set in the \mA-\tanb~parameter space of 
several \ac{MSSM} benchmark scenarios, and in the \cosba-\tanb~parameter space of 
a two Higgs doublet model.

@@

%% Preface
%\begin{preface}
%\end{preface}
%% ToC
\tableofcontents
%\listoffigures
%\listoftables

>>>>

% Abstract
\begin{abstract}%[\smaller \thetitle\\ \vspace*{1cm} \smaller {\theauthor}]
  %\thispagestyle{empty}
The Compact Muon Solenoid (CMS) detector is a general-purpose detector located at the Large Hadron
Collider at CERN. It was designed to test the predictions of the standard model 
and to search for the Higgs boson in addition to searches for new physics beyond
the standard model.
The analyses presented in this thesis are searches for neutral
Higgs bosons with tau leptons in the final state. These searches use proton-proton collision data recorded
by CMS during 2012, 2015 and 2016. The searches are performed in the
context of the minimal supersymmetric standard model (MSSM). One of the analyses, using $19.7\,\invfb$ 
of data collected
during 2012 at $\sqrt{s}=8\,\TeV$, is a search for a heavy neutral Higgs boson
decaying into two $125\,\GeV$ Higgs bosons with standard model-like properties,
with two b-quarks and two tau leptons in the final state. The other analyses use 
$2.3\,\invfb$ of data collected during 2015 and $12.9\,\invfb$ of data collected during 2016, both
at $\sqrt{s}=13\,\TeV$. These are searches for neutral MSSM
Higgs bosons in the mass range of \mbox{$90\,\GeV$--$3.2\,\TeV$} directly decaying
into pairs of tau leptons. 
No significant excess is observed in any of the searches. Upper limits at the 95\% confidence 
level are set on the cross section times branching ratio for the production of Higgs bosons in the MSSM.
In addition, limits are set in the \mA-\tanb~parameter space of 
several MSSM benchmark scenarios, and in the \cosba-\tanb~parameter space of 
a two Higgs doublet model.

@@

%% Preface
%\begin{preface}
%\end{preface}
%% ToC
\tableofcontents
\listoffigures
\listoftables
